\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
	\usepackage{lipsum}    
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\textbox}[1]{%
	\parbox{.333\textwidth}{#1}%
}

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [2] {
    { \textbf{#1} \\ \textit{#2} \\  }
}

\newcommand{\contact} [4] {
    \vspace*{-10pt}
    \begin{center}
        {\huge \scshape {#1}}\\
        #2 \\ #3 \\ #4
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\beginninglist} [4] {
	
	\noindent \textbf{#1} \hfill \hfill #3\\ \noindent \textit{#2} \hfill \hfill #4 \\    
}

\newcommand{\school} [4] {
    \textbf{#1} #2 \\
    #3 #4 \\ 
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

\contact {Rex Oliver}{(803)$-$622$-$7187}{rexoliver12@gmail.com}{github.com/rexoliver}

\header {Education}
\beginninglist {Clemson University} {Bachelor of Science in Computer Science} {GPA: 3.6} {Fall 2017-Spring 2021} \vspace{3pt}

\header {Work Experience}
\beginninglist {Capgemini SE} {Software Engineer} {2021-Present} {Columbia, SC} \vspace{-8pt}
\begin{itemize}
	\item Developed and maintained ASP.NET and vanilla .NET applications for a large defense Company. \vspace{-5pt}
	\item Interracted regularly with the Company's stakeholders to determine their needs, create tickets, and develop solutions to their problems.  \vspace{-5pt}
\end{itemize}
\beginninglist {Clemson University} {IBM Watson in the Watt Researcher} {Fall 2019-Spring 2020} {Clemson, SC} \vspace{-8pt}
\begin{itemize}
	\item Worked with the Clemson Applied Sciences Lab and the Clemson football team to measure speed in a play-by-play manner using Catapult software embedded in the players' padding. \vspace{-5pt}
	\item Contributed to a pipeline that takes the Catapult data from Box to a database in AWS S3. The raw data was then analyzed using Watson to separate the data in a play-by-play manner. \vspace{-5pt}
\end{itemize}	
\beginninglist {Softdocs} {Software Development Intern} {Summer 2019} {Columbia, SC} \vspace{-8pt}
\begin{itemize}
	\item Worked on an Agile Team in front-end development of the Form Builder application. Primarily developed new features for Form Builder in JavaScript using the Knockout.js and Aurelia frameworks. \vspace{-5pt}
	\item Worked with the DevOps team using C\# and .NET to repair failing build systems. \vspace{-5pt}
\end{itemize}	
\beginninglist {Clemson University School of Computing} {Student Ambassador} {Spring 2019-Spring 2020} {Clemson, SC} \vspace{-8pt}
\begin{itemize}
	\item Hosted prospective students and their families on tours and provided a thorough introduction to the school, degree programs, facilities, and research labs.\vspace{-5pt}
	\item Led tour groups of up to 90 people with a presentation and walk-through of the School of Computing. \vspace{-5pt}
\end{itemize}	
\beginninglist {DXC Technology} {Automation Intern} {Summer 2018} {Blythewood, SC} \vspace{-8pt}
\begin{itemize}
	\item Worked with BluePrism and HTML to automate back-end insurance processes and tested these processes on a test SQL server.\vspace{-5pt}
	\item Collaborated regularly with multiple developers in India to create back-end optimizations that helped improve the organization of many internal processes.\vspace{-5pt}
	\item Conducted research on the marketing tactics of insurance companies located in DXC's core market.\vspace{-5pt}
\end{itemize}

\beginninglist {Eureka! Clemson Research Program} {Research Student} {Summer 2017} {Clemson, SC}
\vspace{-8pt}
\begin{itemize}
	\item Participated in a 5 week long research project on programming multiple Roombas to work in the same space in the C programming language.  \vspace{-5pt}
	\item Presented my progress to the rest of the Eureka! progam and many alumni at the end of the program. \vspace{-5pt}
\end{itemize}

\header {Honors and Activities}

\textbf{Honors} \vspace{-5pt}

\begin{itemize}
\item Clemson University Dean's List \hfill \hfill Spring 2018-2021 \vspace{-5pt}  \hspace{10pt}
\item Eagle Scout \hfill \hfill Fall 2015-Present \vspace{-5pt}
\item Cross Country Leadership Award \hfill \hfill Fall 2016 \vspace{-5pt}
\end{itemize}

\textbf{Organizations} \vspace{-5pt}

\begin{itemize}
\item Varsity Cross Country, \textit{Captain} \hfill \hfill Fall 2012-Fall 2016 \vspace{-5pt} 
\item Ultimate Frisbee Club, \textit{Captain} \hfill \hfill Fall 2015-Spring 2017 \vspace{-5pt}  
\item Phi Gamma Delta Fraternity, \textit{Member} \hfill \hfill Fall 2017-2021 \vspace{-5pt} 
\item Clemson Indoor and Outdoor Intramural Soccer \hfill \hfill 2017-2021 \vspace{-5pt} 
\end{itemize}
\header {Technical Skills} 
\textbf{JavaScript (React.js, Knockout.js) \hspace{20pt}   C, C$++$, C\# \hspace{159pt} Java} \\
\textbf{.NET, ASP.NET \hspace{100pt} SQL, MongoDB \hspace{137pt} Python }

\end{document}
